% Begin the document and set up the style of the document
\documentclass[a4paper,11pt]{article}

\usepackage{parskip} % Formatting packages

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\bf\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{3pt}{3pt} % Spacing around sections

\usepackage{lmodern}
\usepackage{fullpage}
\begin{document}
DRW Trading \hfill Keegan Gyoery \break
540 W Madison Street \hfill 15A Point Road \break
Suite 2500 \hfill Northwood, NSW 2066 \break
Chicago, Illinois 60606 \hfill Australia \break
United States of America \hfill keegan.gyoery@gmail.com \break
T +1 312 542 1000 \hfill +61 434 820 971 \break

\vspace{5mm}
\textbf{2020 Summer Trading Internship Application October 18, 2019} \par
To Whom It May Concern, \par

I am writing to apply for DRW’s 2020 Trading Internship. I am in my third year of a
combined Advanced Mathematics and Computer Science degree at the University of New South
Wales. I have maintained a high distinction average throughout my studies and have recently been
included on the 2019 Dean’s Honours List with High Commendation for the School of Computer
Science. With a desire to apply my mathematical skill set to algorithmic trading, I believe I will
be an ideal candidate.\par

DRW is a world leading proprietary trading firm. Working collaboratively to attack complex problems in such a high performance environment is very appealing. I understand that this internship allows each individual to advance their knowledge of financial markets and trading analysis. As a mathematics student with strong quantitative skills, I believe I will thrive in such an environment. I am incredibly curious about financial markets and how I can apply my passion for numbers and problem solving in this competitive industry. Being able to learn on the job is something I look forward to. DRW provides meaningful learning opportunities to highly driven and motivated students. I believe that my mathematics background allows me to learn and apply complex concepts effieciently. Further, the opportunity to work in a team with highly talented individuals is one of my main priorities. The chance to work collaboratively with like-minded individuals is a tantalising prospect.

Through my experience at the tutoring company, HSC CoWorks, I have learnt to work in a collaborative environment, particularly as a leader. I started as a Junior Coach and have since been promoted to Senior Coach where I now work as a Session Leader. The development of junior staff is my responsibility. As such I have developed my communication and interpersonal skills, being able to aid in the training of junior staff whilst maintaining a productive session for students. Further, my skills as a tutor have been recognised as I was recently added to the marking team (previously exclusively qualified HSC teachers). An important skill in any industry is being able to communicate technical jargon to those that are not experienced in your field. Through my development as a tutor I have become very successful at communicating complex mathematical topics to students that are only beginning to gain an understanding of high level mathematics. I believe such communication skills would be sought after and beneficial at DRW.\par

DRW provides a challenging opportunity through which talented students can push themselves and constantly learn in a collaborative environment. I would be pleased to be a part of it. \par

Warm regards, \par

Keegan Gyoery
\end{document}
