% Begin the document and set up the style of the document
\documentclass[a4paper,11pt]{article}

\usepackage{parskip} % Formatting packages

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\bf\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{3pt}{3pt} % Spacing around sections

\usepackage{lmodern}
\usepackage{fullpage}
\begin{document}
\begin{flushright}Keegan Gyoery \break
15A Point Road \break
Northwood, NSW 2066 \break
Australia \break
keegan.gyoery@gmail.com \break
+61 434 820 971 \break
\end{flushright}

\vspace{5mm}
\textbf{2020 Summer Internship Application November 11, 2019} \par
To Whom It May Concern, \par

I am writing to apply for SpaceX’s 2020 Summer Internship. I am about to complete my third year of a combined Advanced Mathematics and Computer Science degree at the University of New South
Wales. I have maintained a high distinction average throughout my studies and have recently been
included on the 2019 Dean’s Honours List with High Commendation for the School of Computer
Science. With a desire to apply my mathematical and programming skill set to space exploration, I believe I will be an ideal candidate.\par

SpaceX is a world leading technology and space exploration company. Working collaboratively to attack complex problems in such a high performance environment is very appealing. I understand that this internship allows each individual to advance their knowledge of technology, and the universe. As a mathematics student with strong quantitative skills, I believe I will thrive in such an environment. I am incredibly curious about space, and the development of technology to sustain life on other planets, and how I can apply my passion for numbers and problem solving in this competitive industry. Being able to learn on the job is something I look forward to. SpaceX provides meaningful learning opportunities to highly driven and motivated students. I believe that my mathematics and computer science background allows me to learn and apply complex concepts effieciently. Further, the opportunity to work in a team with highly talented individuals is one of my main priorities. The chance to work collaboratively with like-minded individuals is a tantalising prospect.

Through my experience at the tutoring company, HSC CoWorks, I have learnt to work in a collaborative environment, particularly as a leader. I started as a Junior Coach and have since been promoted to Senior Coach where I now work as a Session Leader. The development of junior staff is my responsibility. As such I have developed my communication and interpersonal skills, being able to aid in the training of junior staff whilst maintaining a productive session for students. An important skill in any industry is being able to communicate technical jargon to those that are not experienced in your field. Through my development as a tutor I have become very successful at communicating complex mathematical topics to students that are only beginning to gain an understanding of high level mathematics. I believe such communication skills would be sought after and beneficial at SpaceX. Furthermore, my recent work at a small technology start-up has given me an appreciation not only for the requisite skills needed, but also an understanding of how to work collaboratively in a software team.\par

SpaceX provides a challenging opportunity through which talented students can push themselves and constantly learn in a collaborative environment. I would be pleased to be a part of it. \par

Warm regards, \par

Keegan Gyoery
\end{document}
