\documentclass[a4paper,11pt]{article} % Default font size and paper size


\usepackage{xunicode,xltxtra,url,parskip} % Formatting packages
\usepackage{geometry}
\usepackage[usenames,dvipsnames]{xcolor} % Required for specifying custom colors

\usepackage{fullpage} % Margin formatting of the A4 page, an alternative to layaureo can be \usepackage{fullpage}
% To reduce the height of the top margin uncomment: \addtolength{\voffset}{-1.3cm}

\usepackage{hyperref} % Required for adding links	and customizing them
\definecolor{linkcolour}{rgb}{0,0.2,0.6} % Link color
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour} % Set link colors throughout the document

\usepackage{titlesec} % Used to customize the \section command
\titleformat{\section}{\bf\raggedright}{}{0em}{}[\titlerule] % Text formatting of sections
\titlespacing{\section}{0pt}{3pt}{3pt} % Spacing around sections

\usepackage{enumitem}
\setlist[itemize]{noitemsep}

\usepackage{multicol}
\geometry{
	a4paper,
	left=20mm,
	top=20mm,
	right=20mm,
	bottom=20mm
}

\begin{document}

\pagestyle{empty} % Removes page numbering


%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\par{\centering{\huge \textbf{Zachary Sanchez}\par} % Your name

\begin{center}
	0478 683 599 | \href{mailto:zac.sanchez1@gmail.com}{zac.sanchez1@gmail.com} | \url{linkedin.com/in/zachary-sanchez}
\end{center}

\section{CAREER PROFILE}

\begin{itemize}[wide]
	\item Third year, HD average Bachelor of Adv. Math (Hons) / Computer Science student
	\item Experienced in modern software standards and practices 
	\item Effective communicator as a UNSW lab assistant and high school tutor. 
\end{itemize}

\section{EDUCATION}

{\raggedright
\textbf{Bachelor of Adv. Math (Hons) / Comp Sci} \\
\textbf{University of New South Wales} \hfill Mar 2017 - Expected 2021 \\
\textsc{Majors: Applied Mathematics and Computer Science} \\
}
\begin{itemize}[wide]
\item \textbf{WAM: 90.9}
\item 5th in course MATH2221 | 2017 Simon Marais Mathematics Competition Top Quartile
\item Dean's list Faculty of Science 2018 | Dean's list Faculty of Engineering 2018
\end{itemize}
{\raggedright
\textbf{Higher School Certificate} \hfill 2016
}
\begin{itemize}[wide]
	\item \textbf{ATAR: 99.85} | Cadet Officer | St. Vincent's De Paul  | 1st Football | 1st Chess
\end{itemize}

\section{RELEVANT EXPERIENCE AND PROJECTS}
{\raggedright
	\textbf{Intern: Aus Gov. Department of Defence: Science and Technology} \hfill Summer 2018-19
\begin{itemize}[wide]
	\item Developed the backend system for running jobs on a cluster computing network. 
	\item Created user API for producing automatic reports of the data with visualisations and tables. 
	\item Followed test-driven development and version control through \texttt{git}. 
	\item \texttt{python}, \texttt{pytest}, \texttt{pandas}, \texttt{matplotlib}, \texttt{hadoop}, \texttt{pySpark}.
\end{itemize}
{\raggedright
\textbf{Personal Projects} 
}
\begin{itemize}[wide]
	\item \textbf{BitBetter:} Developed a web-based tool for generating statistical analyses of soccer games.
	\item \textbf{AutoBetter:} CL tool for automatically placing bets on a popular betting website.
\end{itemize}
{\raggedright
\textbf{University Projects}
}
\begin{itemize}[wide]
	\item \textbf{COMP3411:} Implemented AI algorithms for a bot to intelligently play a stochastic 2D game. 
	\item \textbf{COMP9444:} Developed neural networks in \texttt{tensorflow} to solve problems in sentiment analysis, image recognition and game playing.
\end{itemize}
{\raggedright
\textbf{Tutor} \\
\textbf{UNSW Computer Science and Engineering} \hfill Feb 2019 - Current
\begin{itemize}[wide]
	\item Lab assistant for COMP1511 (Intro to Programming).
\end{itemize}
\textbf{Talent 100 \url{https://talent-100.com.au/}} \hfill Dec 2017 - Current
}
\begin{itemize}[wide]
\item Conduct engaging weekly lessons in maths and physics 95\% positive feedback
\item Converted outdated materials into \LaTeX \thinspace format and created new material for 2019 syllabus.
\end{itemize}
%----------------------------------------------------------------------------------------
%	EXTRACURRICULAR
%----------------------------------------------------------------------------------------
\section{EXTRACURRICULAR}
\textsc{St Vincent's De Paul (Monthly Night patrol)} | \textsc{Football (Carlton Rovers FC)} 
\section{INTERESTS}
\begin{tabular}{@{}ll}
	\textsc{Board Games}: \small{Casual and Competitive} & \textsc{Investing}: \small{Managing my stock portfolio}
\end{tabular}
\section{REFEREES}

\begin{itemize}[wide]
	\item Timothy Surendonk | Defence Science and Technology | Supervisor
	\item Dr. Jan Zika | UNSW School of Maths and Statistics | MATH2221 Lecturer
	\item David Sadler | Head of Mathematics | Talent 100
\end{itemize}
Contact details available on request
%----------------------------------------------------------------------------------------

\end{document}
